### 2012-12-11 doc/mandc2013/theory_paper/slattery_wilson_evans.tex
fixed subsection headings
mandc updates
fixed typo in mandc paper

\emph{Key Words}: Monte Carlo, domain decomposition, MCSA
\end{small} 
\end{quote}

@@

In order to perform the random walks required to approximate the
summation in Eq~(\ref{eq:adjoint_neumann_solution}), we build
transition probability and weight matrices where probabilities are
column-scaled and the transition weight is defined as:
\begin{equation}
  p_{ij} = \frac{|h_{ji}|}{\sum_j |h_{ji}|}\:,\ w_{ij} =
  \frac{h_{ji}}{p_{ij}},
  \label{eq:adjoint_probability}
\end{equation}
such that we expect to select a new state $j$ from the current state
in the random walk $j$ by sampling column-wise.  Using our result from
Eq~(\ref{eq:inner_product_constraint}) generated by applying the
adjoint constraints, the contribution to the solution in state $i$
from a particular random walk permutation is then:
\begin{equation}
  X_{\nu} = \sum_{m=0}^k W_{m} \delta_{i,i_m}\:,
  \label{eq:adjoint_permutation_contribution}
\end{equation}
where the Kronecker delta indicates that the tally contributes only in
the current state and $b_{i_0}$ will be the sampled source starting
weight. Finally, the expectation value using all permutations is:
\begin{equation}
  E\{X\} = \sum_{\nu} P_{\nu} X_{\nu}\:
  \label{eq:adjoint_expectation_value}
\end{equation}
which if expanded directly recovers the exact solution:
\begin{equation}
  \begin{split}
    E\{X_j\} &=\sum_{k=0}^{\infty}\sum_{i_1}^{N}\sum_{i_2}^{N}\ldots
    \sum_{i_k}^{N} b_{i_0} h_{i_0,i_1}h_{i_1,i_2}\ldots
    h_{i_{k-1},i_k} \delta_{i_k,j} \\ &= x_{j}\:,
  \end{split}
  \label{eq:adjoint_expectation_expansion}
\end{equation}
therefore also providing an unbiased Monte Carlo estimate of the
solution.

@@

\subsection{Iteration Matrix Spectrum}
\label{subsec:iteration_spectrum}

@@

\subsection{Neumann Series Convergence}
\label{subsec:neumann_convergence}

@@

\subsection{Domain Leakage Approximations}
\label{subsec:domain_leak_approx}

@@

\subsection{Random Walk Length}
\label{subsec:walk_length}

@@

\subsection{Domain Leakage}
\label{subsec:domain_leakage}

@@

%%---------------------------------------------------------------------------%%
\section*{ACKNOWLEDGMENTS}

>>>>

\emph{Key Words}: Monte Carlo, domain decomposition, MCSA, parallel
computing
\end{small} 
\end{quote}

@@

In order to perform the random walks required to approximate the
summation in Eq~(\ref{eq:adjoint_neumann_solution}), we build
transition probability and weight matrices where probabilities are
column-scaled and the transition weight is defined as:
\begin{equation}
  p_{ij} = \frac{|h_{ji}|}{\sum_j |h_{ji}|}\:,\ w_{ij} =
  \frac{h_{ji}}{p_{ij}},
  \label{eq:adjoint_probability}
\end{equation}
such that we expect to select a new state $i$ from the current state
in the random walk $j$ by sampling column-wise.  Using our result from
Eq~(\ref{eq:inner_product_constraint}) generated by applying the
adjoint constraints, the contribution to the solution in state $i$
from a particular random walk permutation is then:
\begin{equation}
  X_{\nu} = \sum_{m=0}^k W_{m} \delta_{i,i_m}\:,
  \label{eq:adjoint_permutation_contribution}
\end{equation}
where the Kronecker delta indicates that the tally contributes only in
the current state and $b_{i_0}$ will be the sampled source starting
weight. Finally, the expectation value using all permutations is:
\begin{equation}
  E\{X\} = \sum_{\nu} P_{\nu} X_{\nu}\:
  \label{eq:adjoint_expectation_value}
\end{equation}
which if expanded directly recovers the exact solution:
\begin{equation}
  \begin{split}
    E\{X_j\} &=\sum_{k=0}^{\infty}\sum_{i_1}^{N}\sum_{i_2}^{N}\ldots
    \sum_{i_k}^{N} b_{i_0} h_{i_0,i_1}h_{i_1,i_2}\ldots
    h_{i_{k-1},i_k} \delta_{i_k,j} \\ &= x_{j}\:,
  \end{split}
  \label{eq:adjoint_expectation_expansion}
\end{equation}
therefore also providing an unbiased Monte Carlo estimate of the
solution.

@@

\Subsection{Iteration Matrix Spectrum}
\label{subsec:iteration_spectrum}

@@

\Subsection{Neumann Series Convergence}
\label{subsec:neumann_convergence}

@@

\Subsection{Domain Leakage Approximations}
\label{subsec:domain_leak_approx}

@@

\Subsection{Random Walk Length}
\label{subsec:walk_length}

@@

\Subsection{Domain Leakage}
\label{subsec:domain_leakage}

@@

%%---------------------------------------------------------------------------%%
\section*{ACKNOWLEDGEMENTS}
